Supplemental Information: Gas exchange in large rivers controlled by largest turbulent eddies: implications for remotely sensing gas exchange via SWOT

### 2021-09-10 docs/supp_v4.Rmd
first ms push with hydraulic geometry stuff

##Contents
This supplementary information contains 7 figures and 1 table. Please consult https://github.com/craigbrinkerhoff/RSK600 for all code to build and generate results, figures, and the manuscript.

@@

$A_0$ prior hyperparameters were assigned following an updated version of the method developed by @brinkerhoffConstrainingRemoteRiver2020a. They developed a set of river channel prior hyperparameters for McFLI algorithms that are entirely RS-able and reflect differential channel hydraulics as a function of river geomorphology. They used an extensive database of field measurements and machine learning to identify patterns that associate river width with the hydraulic priors needed to run McFLIs so that prior hyperparameters may be assigned to rivers using only the existing remotely sensed data. For this study, we extracted $\lambda_{A_0}$ and $\gamma_{A_0}$ as the **Xth** percentile values rather than the absolute maximum and minimum values to avoid physically impossible bounds on $A_0$.

@@

>>>>

##Contents
This supplementary information contains 4 texts, 5 figures and 2 tables. Please consult https://github.com/craigbrinkerhoff/RSK600 for all code to build and generate results, figures, and the manuscript.

@@

$A_0$ prior hyperparameters were assigned following an updated version of the method developed by @brinkerhoffConstrainingRemoteRiver2020a. They developed a set of river channel prior hyperparameters for McFLI algorithms that are entirely RS-able and reflect differential channel hydraulics as a function of river geomorphology. They used an extensive database of field measurements and machine learning to identify patterns that associate river width with the hydraulic priors needed to run McFLIs so that prior hyperparameters may be assigned to rivers using only the existing remotely sensed data. For this study, we extracted $\lambda_{A_0}$ and $\gamma_{A_0}$ as the 5th and 95th percentile values rather than the absolute maximum and minimum values to avoid physically impossible bounds on $A_0$.

@@

![Figure S5 All timeseries of k per river](cache/validation/timeseries_noerr.jpg)
